Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
small edit contributions

\title{
Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants
%Counterexample-guided Synthesis of Closed-loop Digital Control Systems
}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

\begin{abstract}
%
Modern control systems are by and large implemented via digital
microcontrollers, which are designed to work in an embedded environment,
within a dynamical plant that can present physical components.
%
This poses a new dimension to the problem of controllers synthesis, which is
classically studied in the digital control literature.
%
In this study, we plan to provide a principled approach to extend this
literature in a number of directions: 
%we are interested in quantitative tasks; 
we focus on automated correct-by-construction synthesis algorithms, as
opposed to verification (or validation) objectives over a designed architecture; 
and we encompass the complete range of
approximations, related to time discretisation, quantisation effects, and
finite-precision representations (with related rounding errors).  To this
end, we propose a CEGIS-based solution that uses inductive 
synthesis in conjunction with a digital verification algorithm to find a
parametric solution for a digital controller given a continuous 
plant specification.
%
\end{abstract}

@@

\item We designed and implemented an automatic approach for 
generating {\em corect-by-construction} digital controllers that is 
based on state-of-the-art inductive synthesis techniques.
Our application of program synthesis is non-trivial 
and requires addressing challenges specific to
control systems such as the effects of quantisers 
and FWL. In particular, we found that a two-stage 
verification engine that continuously refines the precision
of the fixed-point representation is key to the performance of our approach 
yielding, in most cases,  a speed-up  
of several orders of magnitude over 
a conventional one-stage verification 
approach.

@@

%------------------------------------
\subsection{Overview of the Synthesis Process}
\label{verification-flow}
%------------------------------------

@@

The synthesis process is illustrated in Fig.~\ref{DSVerifier_process}. 
A~detailed description of DSVerifier tool can be found
in~\cite{IsmailBCFF15}.  Steps $1$ to $5$ are performed by the
user/synthesiser and Steps~A to D are automatically performed by DSVerifier.
%
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{figures/verification-flow.png}
\vspace{1ex}
\caption{Overview of the synthesis process\label{DSVerifier_process}}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Program Synthesis \\ for Digital Control}

@@

\subsection{Architecture of the program synthesiser}
\label{synthesiser-general}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesiser is of the form
$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.

@@

\subsection{Synthesis for to control}
\label{synthesis-elements}

>>>>

\title{
Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants
%Counterexample-guided Synthesis of Closed-loop Digital Control Systems
}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

\begin{abstract}
%
Modern control systems are by and large implemented via digital
microcontrollers, which are designed to work in an embedded environment,
within a dynamical plant that can present physical components.
%
This poses a new dimension to the problem of controllers synthesis, which is
classically studied in digital control literature.
%
In this study, we plan to provide a principled approach to extend this
literature in a number of directions: we are interested in quantitative
tasks; we focus on automated correct-by-construction synthesis algorithms, as
opposed to verification objectives; and we encompass the complete range of
approximations, related to time discretisation, quantisation effects, and
finite-precision representations (with related rounding errors).  To this
end, we propose a CEGIS-based solution that uses inductive 
synthesis in conjunction with a digital verification algorithm to find a
parametric solution for a digital controller given a continuous 
plant specification.
%
\end{abstract}

@@

\item We designed and implemented an automatic approach for 
generating {\em corect-by-construction} digital controllers that is 
based on state-of-the-art inductive synthesis techniques.
Our application of program synthesis is non-trivial 
and requires addressing challenges specific to
control systems such as the effects of quantisers 
and FWL. In particular, we found that a two-stage 
verification engine that continuously refines the precision
of the fixed-point representation is key to the performance of our approach 
yielding, in most cases,  a speed-up  
of several orders of magnitude over 
a conventional one-stage verification 
engine.

@@

%------------------------------------
\subsection{Overview of the Synthesis Process using DSVerifier}
\label{verification-flow}
%------------------------------------

@@

An overview of the synthesis process is illustrated in
Fig.~\ref{DSVerifier_process}; a detailed description of DSVerifier tool can
be found in~\cite{IsmailBCFF15}.  Steps $1$ to $5$ are performed by the
user/synthesiser and Steps A to D are automatically performed by DSVerifier.
%
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{figures/verification-flow.png}
\vspace{1ex}
\caption{Synthesis process using DSVerifier and the CBMC CEGIS module.}
\label{DSVerifier_process}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Program Synthesis \\ for Digital Controllers}

@@

\subsection{General architecture of the program synthesiser}
\label{synthesiser-general}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesiser is of the form
$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.

@@

\subsection{Synthesis elements specific to control systems}
\label{synthesis-elements}
